---
date: "2019-10-29T11:02:05+06:00"
title: Browse by Region
description: Rank of fraction of heritability for each loci
type: post
weight: 15
---

```{r, echo=FALSE}
library(htmltools)
htmltools::HTML('<script type="text/javascript" src="https://cdn.pydata.org/bokeh/release/bokeh-1.3.4.min.js"></script>')
```

We searched for specific pleiotropic loci that contribute significant non-zero heritability to various phenotypes.
For each locus, we calculated the inflation ratio of the fraction of total heritability, which indicates how many times the locus explains larger amount of heritability than its expected value (${1}\over{N\,of\,segments}$).
Each value means the ratio of fraction of total SNP Heritability to the expected value considering the length of physical distance.


```{r, echo=FALSE}
htmltools::div(class="alert rounded-0 alert-info","
You can hover your mouse on each figure and read information on it. Furthermore, you can magnify a region of interest, check detailed information, and download the figure, etc. using plenty of interactive functions (zoom, pan, reset, save, etc.). You can also click on a phenotype of your interest to get more information.
")
```
Rank of fraction of heritability for each loci.
```{r, echo=FALSE}
htmltools::includeHTML('../../plot_data/byregion_script')
htmltools::includeHTML('../../plot_data/byregion_div')
```