---
author: Somrat
date: "2019-10-29T11:02:05+06:00"
title: Phenotype Network
description: Correlation network of phenotypes
type: post
weight: 20
---

```{r, echo=FALSE}
library(htmltools)
htmltools::HTML('<script type="text/javascript" src="https://cdn.pydata.org/bokeh/release/bokeh-1.3.4.min.js"></script>')
```

We investigated the relationship among the traits included in our analysis using the regional heritability.
For each pair of phenotypes included in our analysis, we calculated the correlation of regional heritability across the entire genome, which can serve as a proxy for the magnitude of pleiotropy between traits.
Note that this correlation differs from the typical SNP-based genetic correlation in that regional heritability does not distinguish positive and negative effects.
However, if we consider a locus as pleiotropic when it affects multiple traits regardless of directions, the regional heritability correlation may reflect the concept of pleiotropy better ([Frei, Oleksandr, et al.](https://www.nature.com/articles/s41467-019-10310-0)).
Using the regional heritability correlation, we rendered a correlation network of traits.

Pairs of traits having higher correlation are linked by thicker edges.
The level of polygenicity of a trait is indicated by the color of the node.
Traits sharing loci are clustered close together as a circle.
Traits of high level of polygenicity are located in the center of the graph, and those of relative low level of polygenicity are located in periphery of it. 

```{r, echo=FALSE}
htmltools::div(class="alert rounded-0 alert-info","
You can hover your mouse on each figure and read information on it. Furthermore, you can magnify a region of interest, check detailed information, and download the figure, etc. using plenty of interactive functions (zoom, pan, reset, save, etc.). You can also click on a phenotype of your interest to get more information.
")
```

```{r, echo=FALSE}
htmltools::includeHTML('../../plot_data/network_script')
htmltools::includeHTML('../../plot_data/network_div')
```